### 2021-11-10 manuscript.Rmd
Change to order of authors
I think this is a better reflection of the contribution

author: 
  - name          : "Christoph Stahl"
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Herbert-Lewin-Straße 2, 50931 Köln"
    email         : "christoph.stahl@uni-koeln.de"
  - name          : "Marius Barth"
    affiliation   : ""
  - name          : "Hilde Haider"
    affiliation   : ""

>>>>

author:
  - name          : "Marius Barth"
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Herbert-Lewin-Straße 2, 50931 Köln"
    email         : "christoph.stahl@uni-koeln.de"
  - name          : "Christoph Stahl"
    affiliation   : ""
  - name          : "Hilde Haider"
    affiliation   : ""
